%
% File: dedication.tex
% Author: Tengxiang Li
%
\chapter{Author's dedication}
\begin{SingleSpace}


\noindent\hspace{2em}We, the authors of this thesis, wholeheartedly dedicate this work to Astana IT University, an institution that has not only provided us with quality education but also instilled in us a sense of responsibility and purpose as future professionals in the field of cybersecurity. The academic environment fostered by the university challenged us to think critically, act ethically, and contribute meaningfully to the evolving landscape of information security. We are especially grateful for the university’s emphasis on combining theoretical understanding with practical application, which was instrumental in shaping the dual focus of this research.

Our deepest appreciation goes to our thesis supervisor, Ms. Gulsim Tulepova, whose expert guidance, insightful feedback, and unwavering support were pivotal throughout every phase of this work. Her dedication to academic excellence, her high standards, and her constant encouragement motivated us to reach beyond the minimum and strive for quality and relevance in our research.

This thesis stands as a testament to the knowledge and mentorship we received during our time at the Department of Cybersecurity. It is our sincere hope that this work will contribute to the academic discourse at Astana IT University and serve as a resource for future students and researchers exploring security standards and policy development.

\end{SingleSpace}
\clearpage